---
title: "Testing portfolio allocation with 沪深300一级行业全收益指数"
author: "hfwang"
date: "2020/6/17"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries, include=FALSE}
## include = FALSE means to have the chunk evaluated, but neither the code nor its output displayed.

library(xts)
library(lubridate)
library(quantmod)
library(TTR)
library(PerformanceAnalytics)
library(gridExtra)

source("cal_ret.R")
setwd("E:/My_Programs/allocation_models")

```

### Read data

read data from local csv files, data downloaded previously from yahoo Finance. 

```{r read local data}
s_index_data.raw<-read.csv("data/沪深一级行业全收益序列200707-202006.csv")

```

```{r convert to xts format, include=FALSE}
s_index_data<-na.locf(xts(s_index_data.raw[,-1],ymd(s_index_data.raw[,1]))) 

s_index.ret<-na.omit(ROC(s_index_data))

```

```{r begin/end dates, echo=FALSE}
begin_date<-start(s_index.ret)
end_date<-end(s_index.ret)

```


### read benchmark portfolio returns
read 60/40 benchmark generated with 沪深300全收益 and 上证10年国债全收益指数 ("benchmark")

```{r generate benchmark}

benchmark.raw<-read.csv("data/benchmark_60_40_沪深300全收益上证10年国债.csv")
## this is already return data
benchmark.ret<-na.locf(xts(benchmark.raw[,-1],ymd(benchmark.raw[,1]))) 

csi300.raw<-read.csv("data/上50沪深300全收益指数.csv")
csi300.ret<-xts(csi300.raw[,-1], ymd(csi300.raw[,1]))$H00300.CSI
csi300.ret<-na.omit(ROC(csi300.ret))
```

generate equal weight portfolio with ten sectors ("portfolio")

```{r general equal weight portfolio}
portf.ret<-Return.portfolio(s_index.ret,rebalance_on="months", verbose=T)
```

generate naive risk parity portfolio with weights being the inverse of previous month volatility

```{r generate naive risk parity portfolio}
risk_parity.ret<-portf.naive_risk_parity(s_index.ret, verbose=T)
```

```{r combine asset returns and benchmark returns, include=FALSE}
##combine asset returns and benchmark returns

all.ret<-na.omit(cbind(portf.ret$returns,risk_parity.ret$returns, benchmark.ret,csi300.ret))
colnames(all.ret)<-c("Equal_weight","Risk_parity","Sixty_fourty", "CSI300")

```


```{r read table info, include=FALSE}
## read asset names
index_csv<-read.csv("wind_data/沪深300一级全收益指数.csv")

index_csv<-na.omit(index_csv)
index_csv<-data.frame(index_csv)

```

#### 标的名称和代码

```{r print table info, echo=FALSE}
index_csv$SEC_ENGLISHNAME<-NULL
grid.table(index_csv)

```


### Generate Performance   

#### Data from `r begin_date` to `r end_date`

#### Correlation Matrix

```{r correlation matrix, echo=FALSE}
round(cor(s_index.ret),2)
round(cor(all.ret),2)
```


#### Performance Summary

```{r performance Charts of Raw Data, echo=TRUE}
charts.PerformanceSummary(s_index.ret, date.format="%Y%m", main="asset returns")

charts.PerformanceSummary(all.ret, date.format="%Y%m", main="Benchmark Portfolios")

all_asset.ret<-cbind(s_index.ret,portf.ret$returns,risk_parity.ret$returns)

tab.perf(all_asset.ret["20120912/"])

tab.perf(all.ret["20120912/"])


```

Portfolio Calendar Year Returns

```{r all portfolio annual returns, echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(s_index.ret,colnames(s_index.ret))


cal_annual_ret<-gen_cal_annual_ret(all.ret,colnames(all.ret))

cal_annual_ret
```

Equal weight portfolio Calendar Date Returns 

``` {r equal weight calendar return, echo=FALSE}
cal<-calendar_ret(portf.ret$returns)
cal

```

Equal Weight Portfolio Weights over time

```{r equal weight portfolio weights, echo=FALSE}

chart.StackedBar(portf.ret$BOP.Value,date.format="%y/%m", colorset=rainbow12equal, border=NA)
```

Naive Risk Parity Portfolio Calendar Date Returns 

``` {r naive risk parity calendar return, echo=FALSE}
cal<-calendar_ret(risk_parity.ret$returns)
cal
```

Naive Risk Parity Portfolio Weights over time

```{r naive risk parity portfolio weights, echo=FALSE}

chart.StackedBar(risk_parity.ret$BOP.Value,date.format="%y/%m", colorset=rainbow12equal, border=NA)
```
